### 2022-05-25 Manuscript/Manuscript.tex
Add image versions, non-submission latex

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{changepage}
\usepackage[utf8x]{inputenc}
\usepackage{textcomp,marvosym}
\usepackage{cite}
\usepackage{nameref,hyperref}
\usepackage[right]{lineno}
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }
\usepackage[table]{xcolor}
\usepackage{array}
\newcolumntype{+}{!{\vrule width 2pt}}
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in
\textheight 8.75in
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}
\bibliographystyle{plos2015}
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
%\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
%\setlength{\headheight}{27.023pt}
%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}

%% ADDED BY AUTHORS
\usepackage{orcidlink}
\makeatletter
\renewcommand {\verbatim@font}
{%
  \fontencoding {T2A}%
  \fontfamily
  {\ttdefault}%
  \selectfont
}
\makeatother
\usepackage [russian,english] {babel}
%% END ADDED BY AUTHORS

@@

\end{flushleft}
\section*{
Abstract
}
The skill to recognize and classify taxa requires knowledge that is less and less common in the scientific community. At the same time, it is clear that these skills are needed in biodiversity monitoring for management and conservation, especially when carried out by citizen scientists. Formalizing the required knowledge in digital identification keys is a way of making such knowledge more available for professional and amateur observers of biodiversity. In this paper we describe Clavis, a modern open framework for capturing knowledge required for taxon identification through digital keys, allowing for a level of detail beyond that of any current format. We exemplify each concept using Pokémon as a fictional taxonomic group.
\linenumbers
\section*{
Introduction
}
Distinguishing biological taxa from one another is a necessity in biodiversity monitoring. As species are going extinct at an unprecedented rate~\cite{Ceballos2015, Johnson2017}, we need to monitor as much as we can to identify statuses and trends. Meanwhile, research and management is currently facing a ``taxonomic impediment'', where taxonomic knowledge is disappearing from the scientific community~\cite{Engel2021}.

@@

\begin{figure}[!h]
  \caption{{\bf The core concepts of any Clavis key.}
  \underline{Taxa} (left) and \underline{characters} (right) are connected through \underline{statements} (center). Each statement refers to one taxon and one character, linking the two by a value, usually one of the possible \underline{states} of the character, or a numerical value.}
  \label{fig1}
\end{figure}

@@

\begin{figure}[!h]
  \caption{{\bf The identification of a specimen.}
  When considering all taxa, the character about size is not relevant, as one of the taxa has no statement for size, so only the character about colors is relevant (a). The user gives an input, which is compared to the related statements, upon which 2 taxa are eliminated (b). Considering the now remaining taxa, the character about size has become relevant (c). The user gives another input, and based on the related statements, one additional taxon is eliminated, leaving one result (d).
  }
  \label{fig2}
 \end{figure}

@@

\begin{figure}[!h]
  \caption{\textit{\textbf{A taxon tree of the Pikachu-line}:
Taxa tagged as endpoint are indicated with an asterisk (*). This key continues until the correct morph (``Shiny'' or default) is known, while differences in the sexes are optional and will not be asked about once the correct Pokémon and morph have been determined.
  }}
  \label{fig3}
\end{figure}
\subsection*{
Characters, statements and frequencies
}
One of the possible values for a statement (the relationship between a taxon and a character) is the id of a state. This statement also may have a frequency: the proportion of cases where individuals of this taxon have this state for this character. It can be set to 0 or 1 or any value in between.

@@

\begin{figure}[!h]
  \caption{\textit{\textbf{The colors of Pikachu and Raichu}:
By adding statements for the non-exclusive character for the color of Pikachu and Raichu, the user can pick and/or exclude freely from a list of colors in the identification key.
}}
 \label{fig4}
\end{figure}

@@

\begin{figure}[!h]
  \caption{{\bf An example implementation of a Clavis key graphical user interface.}
A hierarchical list of taxa (left) is reduced by providing input on characters (right). Only characters relevant for all remaining taxa are shown.
}
  \label{fig5}
\end{figure}

@@

\section*{
Data availability and licensing
}
The latest formal definition of Clavis can be found at \url{https://github.com/Artsdatabanken/Clavis}. All files related to this manuscript can be found at \url{https://github.com/WouterKoch/Clavis}.

>>>>

\documentclass[10pt,letterpaper]{article}
\usepackage{amsmath,amssymb}
\usepackage{changepage}
\usepackage[utf8x]{inputenc}
\usepackage{textcomp,marvosym}
\usepackage{cite}
\usepackage{nameref,hyperref}
\usepackage[left]{lineno}
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }
\usepackage[table]{xcolor}
\usepackage{array}
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}
\bibliographystyle{plos2015}
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\usepackage{orcidlink}
\makeatletter
\renewcommand {\verbatim@font}
{%
  \fontencoding {T2A}%
  \fontfamily
  {\ttdefault}%
  \selectfont
}
\makeatother
\usepackage [russian,english] {babel}

\hypersetup{
  colorlinks   = true,
  urlcolor     = black,
  linkcolor    = black,
  citecolor   = black
}

@@

\end{flushleft}
\section*{
Abstract
}
The skill to recognize and classify taxa requires knowledge that is less and less common in the scientific community. At the same time, it is clear that these skills are needed in biodiversity monitoring for management and conservation, especially when carried out by citizen scientists. Formalizing the required knowledge in digital identification keys is a way of making such knowledge more available for professional and amateur observers of biodiversity. In this paper we describe Clavis, a modern open framework for capturing knowledge required for taxon identification through digital keys, allowing for a level of detail beyond that of any current format. We exemplify each concept using Pokémon as a fictional taxonomic group.
\section*{
Introduction
}
Distinguishing biological taxa from one another is a necessity in biodiversity monitoring. As species are going extinct at an unprecedented rate~\cite{Ceballos2015, Johnson2017}, we need to monitor as much as we can to identify statuses and trends. Meanwhile, research and management is currently facing a ``taxonomic impediment'', where taxonomic knowledge is disappearing from the scientific community~\cite{Engel2021}.

@@

\begin{figure}[!h]
  \includegraphics[width=\textwidth]{Images/Fig1}
  \caption{{\bf The core concepts of any Clavis key.}
  \underline{Taxa} (left) and \underline{characters} (right) are connected through \underline{statements} (center). Each statement refers to one taxon and one character, linking the two by a value, usually one of the possible \underline{states} of the character, or a numerical value.}
  \label{fig1}
\end{figure}

@@

\begin{figure}[!h]
  \includegraphics[width=\textwidth]{Images/Fig2}
  \caption{{\bf The identification of a specimen.}
  When considering all taxa, the character about size is not relevant, as one of the taxa has no statement for size, so only the character about colors is relevant (a). The user gives an input, which is compared to the related statements, upon which 2 taxa are eliminated (b). Considering the now remaining taxa, the character about size has become relevant (c). The user gives another input, and based on the related statements, one additional taxon is eliminated, leaving one result (d).
  }
  \label{fig2}
 \end{figure}

@@

\begin{figure}[!h]
  \includegraphics[width=\textwidth]{Images/Fig3}
  \caption{\textit{\textbf{A taxon tree of the Pikachu-line}:
Taxa tagged as endpoint are indicated with an asterisk (*). This key continues until the correct morph (``Shiny'' or default) is known, while differences in the sexes are optional and will not be asked about once the correct Pokémon and morph have been determined.
  }}
  \label{fig3}
\end{figure}
\subsection*{
Characters, statements and frequencies
}
One of the possible values for a statement (the relationship between a taxon and a character) is the id of a state. This statement also may have a frequency: the proportion of cases where individuals of this taxon have this state for this character. It can be set to 0 or 1 or any value in between.

@@

\begin{figure}[!h]
  \includegraphics[width=\textwidth]{Images/Fig4}
  \caption{\textit{\textbf{The colors of Pikachu and Raichu}:
By adding statements for the non-exclusive character for the color of Pikachu and Raichu, the user can pick and/or exclude freely from a list of colors in the identification key.
}}
 \label{fig4}
\end{figure}

@@

\begin{figure}[!h]
  \includegraphics[width=\textwidth]{Images/Fig5}
  \caption{{\bf An example implementation of a Clavis key graphical user interface.}
A hierarchical list of taxa (left) is reduced by providing input on characters (right). Only characters relevant for all remaining taxa are shown.
}
  \label{fig5}
\end{figure}

@@

\section*{
Data availability and licensing
}

The latest formal definition of Clavis can be found at \url{https://github.com/Artsdatabanken/Clavis}. All files related to this manuscript can be found at \url{https://github.com/WouterKoch/Clavis}.

### 2022-05-25 Manuscript/S1 - Clavis schema.tex
Add image versions, non-submission latex

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{changepage}
\usepackage[utf8]{inputenc}
\usepackage{textcomp,marvosym}
\usepackage{cite}
\usepackage{nameref,hyperref}
\usepackage[right]{lineno}
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }
\usepackage[table]{xcolor}
\usepackage{array}
\newcolumntype{+}{!{\vrule width 2pt}}
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in
\textheight 8.75in
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}
\bibliographystyle{plos2015}
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
%\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
%\setlength{\headheight}{27.023pt}
%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}

%% ADDED BY AUTHORS
\usepackage{orcidlink}
\makeatletter
\renewcommand {\verbatim@font}
{%
  \fontencoding {T2A}%
  \fontfamily
  {\ttdefault}%
  \selectfont
}
\makeatother
\usepackage [russian,english] {babel}

\usepackage{newunicodechar}
\newunicodechar{♀}{\Female}
\newunicodechar{♂}{\Male}

%% END ADDED BY AUTHORS

@@

    "regionName": {
      "description": "The name of the region for which the key is valid
(e.g. covers all subtaxa).",

@@

all subtaxa), represented as the coordinates array of a GeoJSON

@@

      "description": "The id(s) of the publising institutions of the

@@

      "comment": "Taxa to which the key can resolve. Either the taxa
directly or their children. SubTaxonomic taxa (such as morphs, genders,
life stages) should be presented through their parent only.",
Lowercase alphanumerical and underscores are allowed.",
Lowercase alphanumerical and underscores are allowed.",
Lowercase alphanumerical and underscores are allowed.",
Lowercase alphanumerical and underscores are allowed.",
Lowercase alphanumerical and underscores are allowed.",
Lowercase alphanumerical and underscores are allowed.",
Lowercase alphanumerical and underscores are allowed.",
requirement. Lowercase alphanumerical and underscores are allowed.",
Lowercase alphanumerical and underscores are allowed.",
          "description": "The id(s) of the publising institutions of the
media file.",

@@

@@

@@

          "description": "Reference to a taxon at a provider, as an
object wiht a provider id and a taxon id at that provider.",

@@

represented as the coordinates array of a GeoJSON MultiPolygon.",
        "geographyService": {
distribution information for this taxon.",

@@

are catagorical and mutually exclusive, non-exclusive when these are

@@

          "comment": "Only to be used for catergorical characters.

@@

        "taxonId",
        "characterId",

@@

property, represented as the coordinates array of a GeoJSON
        "geographyService": {
distribution information for this property.",

@@

\end{verbatim}
\nolinenumbers
\end{document}

>>>>

\documentclass[10pt,letterpaper]{article}
\usepackage{amsmath,amssymb}
\usepackage{changepage}
\usepackage[utf8]{inputenc}
\usepackage{textcomp,marvosym}
\usepackage{cite}
\usepackage{nameref,hyperref}
\usepackage[left]{lineno}
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }
\usepackage[table]{xcolor}
\usepackage{array}
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}
\bibliographystyle{plos2015}
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\usepackage{orcidlink}
\makeatletter
\renewcommand {\verbatim@font}
{%
  \fontencoding {T2A}%
  \fontfamily
  {\ttdefault}%
  \selectfont
}
\makeatother
\usepackage [russian,english] {babel}

\hypersetup{
  colorlinks   = true,
  urlcolor     = black,
  linkcolor    = black,
  citecolor   = black
}
\usepackage{newunicodechar}
\newunicodechar{♀}{\Female}
\newunicodechar{♂}{\Male}

@@

all subtaxa), represented as a geography object.",
      "$ref": "#/definitions/geography"
      "description": "The id(s) of the publishing institutions of the
      "comment": "Taxa to which the key can resolve (either the taxa
directly or their children).",
  "additionalProperties": false,
      "additionalProperties": false
Lowercase alphanumeric and underscores are allowed.",
Lowercase alphanumeric and underscores are allowed.",
Lowercase alphanumeric and underscores are allowed.",
Lowercase alphanumeric and underscores are allowed.",
Lowercase alphanumeric and underscores are allowed.",
Lowercase alphanumeric and underscores are allowed.",
Lowercase alphanumeric and underscores are allowed.",
requirement. Lowercase alphanumeric and underscores are allowed.",
Lowercase alphanumeric and underscores are allowed.",
          "description": "The id(s) of the publishing institutions of
the media file.",
      "additionalProperties": false
      "additionalProperties": false
      "description": "A geographic element (name, polygon, and/or
external service).",
          "description": "The name of the area(s).",

@@

        "polygon": {
          "description": "The geographical area(s), represented as the
coordinates array of a GeoJSON MultiPolygon.",

@@

        "service": {
geographical information.",

@@

      "additionalProperties": false

@@

      "additionalProperties": false

@@

          "description": "Description of the service.",

@@

          "description": "Reference to a taxon at one or more providers,
each as an object with a provider id and a taxon id at that provider.",
          "comment": "Accepts an array for multiple sources. Each
element accepts an object for multilingual support.",

@@

represented as a geography object.",
          "$ref": "#/definitions/geography"
      "additionalProperties": false

@@

are categorical and mutually exclusive, non-exclusive when these are

@@

          "comment": "Only to be used for categorical characters.

@@

        "taxon",
        "character",

@@

property, represented as a geography object.",
          "$ref": "#/definitions/geography"

@@

      "additionalProperties": false
\end{verbatim}
\nolinenumbers
\end{document}
